The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
more hab selection

<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or features by animals [@Manly_1993; @Boyce_1999]. Combined,
social structure and habitat selection are intimately linked as individuals must
share space to interact and distribution of resources influence home range size
and group dynamics [@Webber_2018]. <!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.

>>>>

<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999]. Combined,
social structure and habitat selection are intimately linked as individuals must
share space to interact and the distribution of resources influences home range size
and group dynamics [@Webber_2018].

Habitat selection is a scale-sensitive process
Animals select habitats at multiple scales

<!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
